### 2019-08-05 chapters/3-background.tex
Add todo messages
Add figures with Stackoverflow Developer Survey Information
Add funnel with number of modules for each stage of the experiment
Add code example for run-time information gathering

\chapter{Background}\label{chap:background}
Explain the general context of your work.
Explain mathematical background required and introduce notation.
\input{figures/background/algBackpropagation}
\input{figures/background/figTikz}

\section{JavaScript}
\subsection{TypeCoercion}
\subsection{NPM Packages}

\section{TypeScript}
\subsection{Declaration Files}
\subsection{Definitely Typedd}

\section{Jalangi}

>>>>

\chapter{Background}\label{chap:background}
Explain the general context of your work.
Explain mathematical background required and introduce notation.

\section{JavaScript}
\todo{Agregar img con data de la survey de stackoverflow indicando la popularidad de JS. Agarrar data de encuestas viejas y hacer una comparación de agunas techs, tipo JS, PHP, Python, Java, etc.}

\todo{Talvez agregar}
\input{figures/background/stackoverflowSurvey-ProgrammingLanguages2019.tex}

\input{figures/background/stackoverflowSurvey-ProgrammingLanguagesEvolution.tex}

\todo{Agregar tema serverless. Que NodeJS tiene el 75\% de los deploys}

\subsection{TypeCoercion}
\todo{Hablar de WTFS}
\todo{Aca incluir texto de what does it mean to be a JS Type}
\subsection{NPM Packages}
\todo{Agregar info de NPM by numbers! Cuantos downloads, cuantos packages, etc.}
\todo{https://snyk.io/blog/npm-passes-the-1-millionth-package-milestone-what-can-we-learn/}

\section{TypeScript}
\subsection{Declaration Files} \label{sec:declaration-files-background}
\subsection{Definitely Typedd}

\section{Jalangi} \label{sec:jalangi}

### 2019-08-05 chapters/4-approach.tex
Add todo messages
Add code example for run-time information gathering

\chapter{Approach}\label{chap:approach}
The approach starts with the problem definition and continues with what you have done. Try to give an intuition first and describe everything with words and then be more formal like `Let $g$ be ...'.

Strive to make the following items crystal clear to your readers.
\begin{itemize}
\item What is the problem you are treating?
\item What are the research questions you want to answer in this work?
\item What are your own contributions and what is work of others? If
  you are working in a team, it is important to demarcate against the
  contributions of others in your team.
\end{itemize}

Describe each major technical problem and how it was solved.

\section{Problem Definition}
\todo{JavaScript popularity has increased dramatically over the last years. TypeScript has evolved naturally as the professional way of developing code in JavaScript, providing the robustness that ervery compiled language has. Generating the declaration files manually is very time consuming and error prone.}

\todo{NodeJS, frameworks like React, Angular, Vue. The migation to Single Page Apps and Serverless, etc.}

\todo{Info from Stackoverflow and Github}

\todo{Mention DefinitelyTyped repository. Explicar claramente que el objetivo de esta tesis es generar }

\todo{El objetivo es solucionar el problema de definitely typed!!! Por eso se usa como objetivo que el input sea un node module}

\section{TypeScript Declaration Files Generation Method}
\todo{Explain overview process for generating declaration file.  Explain that the focus of this thesis was to focus on the runtime information and use the symbolic executor as a 'refinement' of the test cases. Use 'public' document of the Master project}

This Thesis introduces a \textit{TypeScript Declaration Files Generation Method}, which generates a valid TypeScript Declaration File for a specific NPM package, as explained in Fig. \ref{fig:tsd_generation_method_block_diagram}.

\input{figures/approach/typescriptDeclarationFilesGenerationMethodBlockDiagram}

Following the goal of easing and automating the generation of TypeScript Declaration Files for existings JS Libraries, the method receives the name of the JS Library published to the NPM Registry as an input argument and returns the corresponding TypeScript declaration file.

The method consists of a continuous refinement process. It generates a TypeScript Declaration File based on data flow and type information gathered at run-time from a code base that executes the JS Library. A Symbolic Execution Engine expands the code base in every iteration by generating new test cases that explore different execution paths.

The file generated after each iteration is a valid and fully functional declaration file, suitable for usage in development environments. It contains no errors, matches the structure of the corresponding JS Library and could be uploaded to the DefinitelyTyped Repository. It is therefore intended to be integrated within the build process of the JS Library.

\todo{Decir que para la tesis se decidio no inlcuir el feedback loop. Solo se hizo la parte de runtime, etc.}

\subsection{Overview}
As explained before, the DefinitelyTyped Repository is the official repository for finding declaration files for npm packages. Therefore, the \textit{TypeScript Declaration Files Generation Method} is intended to be used on existing, published npm packages. The generated output TypeScript declaration file is a valid file which can be used for development and uploaded to the DefinitelyTyped Repository.

The method uses an instrumentation framework to gather data flow information and type information at runtime. A second independent block uses the gathered information to generate a TypeScript Declaration File. The signatures obtained from the generated declaration file are used to generate pre and post conditions on a Symbolic Execution Engine in order to build different test cases that explore new execution paths. The code from the test cases is then added to the existing code base. The declaration file is generated again using an expanded code base.

A feedback loop refines iteratively the outcome by combining run-time information gathering and symbolic analysis: It performs Run-Time Analysis to generate a declaration file using run-time information and a Symbolic Execution Engine to refine and expand the code base being used to gather run-time information.

Running the TypeScript Declaration File Generation Tool with the same run-time information as input will always produce the same result. If new execution paths are covered by the test cases, new run-time information will be gathered and the declaration file will change accordingly. In order to obtain a sound analysis, this feedback loop would be iterated until there are no differences among the generated declaration files. However, by trading soundness for scalability, the overall procedure can be stopped either using a loop bound, a time bound or an heuristics mechanism. Exploring and investigating the proper stopping criteria is beyond the scope of this work.

Finally, the generated declaration files are fully functional and valid files. They can be used in a TypeScript project without further modifications

\subsection{Implementation}
\todo{Decir que es un framework. Decir que es tipo una pipeline donde todo se conecta con lo otro. Explicar que por mas que reciba un string como input}

\section{Initial code base}

\section{Run-time Information Gathering} \label{run-time-information-gathering}
\subsection{Instrumentation}
\subsubsection{Interactions}
\todo{inputValue}
\todo{getField}
\todo{putField}
\todo{methodCall}
\todo{usedAsArgument}
\todo{convertedTo}

\subsubsection{Wrapper Objects}
\todo{Proxy Objects}
\todo{Primitives}
\todo{Null}
\todo{Undefined}
\subsection{Output Format}
\todo{Explicar que es un JSON con todas las interactions. Explicar estructura de cómo se forma el JSON}
\subsection{Blacklisted Modules}
\todo{Incluir grafico con los blacklisted modules}

>>>>

\chapter{Approach}\label{chap:approach}

\section{Problem Definition}
In spite of the fact that JavaScript was originally intended for simple web-pages scripting, it's popularity has increased over the last years, being the most commonly used programming language among professional developers in 2018. Development of robust and high-quality frameworks such as jQuery, AngularJS, React or Vue.js contributed to JavaScript being the leading programming language for client-side development.

Moreover, several back-end applications are being written in JavaScript using Node.js, thus unifying the programming languages of client and back-end code. Companies with architectures based on concepts such as serverless and microservices are moving traditional back-end code written in Java, Python or PHP to the cloud and replacing it by small compute services, like AWS Lambda or Google Cloud Functions, or directly by cloud managed services. It is very common that development teams decide to write the compute services in Node.js, thus reducing the technological stack.

However, JavaScript was not intented for developing large-scale applications. Lack of good interface descriptions using types and unintuitive type coercion have been slowing development of JavaScript applications.

The TypeScript programming language is a superset of JavaScript with optional type annotations that compiles to plain JavaScript. It has become a widely used alternative for JavaScript. It enables IDEs to perform code intelligence tasks such as code completion, code navigation or refactoring and it rules out possible run-time errors through static type checking.

Aware that types are important for developing maintainable software systems, several industrial developers started using TypeScript in JavaScript projects. However, despite TypeScript's popularity, many new and existing JavaScript Libraries are still being written in pure JavaScript.

The possibility of using exissting JS libraries in TypeScript projects is critical for a smooth transition and for its adoption in industrial development. TypeScript enables it through \textit{declaration files}, a typed description of the library's API. A public repository, DefinitelyTyped \citep{definitely-typed-repository}, contains declaration files for more than 6000 JS Libraries. 71\% of the top 1000 depended-upon packages have their corresponding declaration file in DefinitelyTyped, as explained in \chapref{chap:background}.

Unfortunately, such files are written and maintained manually, which is tedious, error prone and highly time consuming. The evolution of the declaration files does not follow in some cases the continous development of the corresponding libraries. As a result, some declaration files end up being out of date, thus hindering their usability. Mismatches between the declaration files and the actual JavaScript Library code have a negative impact on developers. Type checking messages and IDE code intelligence features are not accurate, thus increasing developing costs, generating actually more difficulties than before migrating to TypeScript.

Declaration files are critical for TypeScript projects. TypeScript's popularity increase and the continuous growth of packages uploaded to the NPM registry, surpassing \textit{1 million} packages by June 2019, indicate that mismatches between declaration files and JavaScript implementations will likely grow. This Thesis tackles the declaration file generation problem and proposes a solution for assiting programmers in creating TypeScript Declaration Files from JavaScript code and keeping them up to date after.

\todo{Agregar una imagen de un modulo simple con codigo JavaScript y que del otro lado salga el declaration file.}

\section{TypeScript Declaration Files Generation Method}

We introduce a \textit{TypeScript Declaration Files Generation Method}, which generates a valid TypeScript Declaration File for a specific JavaScript Library uploaded to the NPM Registry, as explained in \figref{fig:tsd_generation_method_block_diagram}.

\input{figures/approach/typescript-declaration-files-generation-method/typescriptDeclarationFilesGenerationMethodBlockDiagram.tex}

The method consists of a continuous refinement process. It generates a TypeScript Declaration File based on data flow and type information gathered at run-time from a code base that executes the JavaScript Library. The code base is expanded by a Symbolic Execution Engine that generates test cases using the generated type definitions. As a result, new execution paths are explored, gathering new run-time information and thus refining the declaration file in every iteration.

Following the goal of easing and automating the generation of TypeScript Declaration Files for existings JavaScript Libraries, the method receives the name of the JavaScript Library published to the NPM Registry as an input argument and returns the corresponding TypeScript declaration file.

The declaration file returned by the method is valid and fully functional, making it suitable for being used within the development process. It contains no errors and matches the structure of the JavaScript Library under analysis, so that the JavaScript code generated after compilation runs. The conducted experiments included tests that consisted on replacing a specific type definition from DefinitelyTyped \citep{definitely-typed-repository} with the one generated in the experiments: TypeScript compilation was sucessful, the generated JavaScript code ran without errors and code intelligence features performed by IDEs like code completion worked as expected.

The feedback loop was not included in the implementation, though. As explained, exploring new execution paths by creating new test cases will refine the declaration files: new types will be assigned to different variables, new interfaces will be detected and existing interfaces will be defined more accurately by detecting new properties. From an incremental point of view, generating the declaration files from run-time information has to be developed in a first place. A declaration file must exist first so that it can be refined afterwards.

For that reason, the decision was to keep the focus on building an end-to-end architecture that supports the generation of valid declaration files for a specific JavaScript Library. The proposed architecture supports a future addition of the refinement loop, without modifying the existing blocks. The Symbolic Execution Engine will expand the existing code base by generating new test cases. The actual generation of declaration files remains unmodified.

\subsection{Implementation}
As explained before, the DefinitelyTyped Repository is the official repository for finding declaration files for existing JavaScript Libraries. The \textit{TypeScript Declaration Files Generation Method} is intended to be used on existing, published npm packages. The generated output TypeScript declaration file is a valid file which can be used for development and uploaded to the DefinitelyTyped Repository.

Code examples that execute the JavaScript Library are needed to extract the run-time information via code instrumentation. It is achieved by retrieving the examples provided in the README files of the repositories of the different libraries. This is generally the place where developers explicitely show how to use their code. It showed to be an appropriate and pragmatic way of extracting the developer's intention and providing an useful initial code base with meaningful examples, thus avoiding a possible cold start problem.

The examples and the code base of the library are instrumented with Jalangi \citep{DBLP:conf/sigsoft/SenKBG13}\citep{DBLP:conf/sigsoft/SenKBG13a} to gather data flow information and type information at runtime. Jalangi is a dynamic analysis configurable framework that provides several analysis modules that were extended as needed to retrieve the required run-time information, which is then saved to an output JSON file. This block is written in JavaScript and it runs in Node.js within a Docker container.

A second independent block uses the run-time information to generate a TypeScript Declaration File. It infers the overall structure of the JS Library, the interfaces and the types from the JSON file. This block is a Node.js application written in TypeScript that also runs within a Docker container.

The signatures obtained from the generated declaration file are used to generate pre and post conditions on a Symbolic Execution Engine in order to build different test cases that explore new execution paths. The code from the test cases is then added to the existing code base and the declaration file is generated again using an expanded code base.

Running the TypeScript Declaration File Generation Tool with the same run-time information as input will always produce the same result. If new execution paths are covered by the test cases, new run-time information will be gathered and the declaration file will change accordingly. In order to obtain a sound analysis, the feedback loop would be iterated until the generated declaration files in consecutive iterations do not differ. However, by trading soundness for scalability, the overall procedure can be stopped either using a loop bound, a time bound or an heuristics mechanism.

\todo{Agregar una imagen mostrando que es un unico script que hace todo. Mostrar imagenes de docker mostrando en qué está escrito cada cosa.}

\section{Initial code base}
To extract run-time information of a JavaScript Library, it is necessary, by definition, to actually execute the code. It is not enough to instrument the source files of the library. The analysis modules provided by Jalangi to gather information are only triggered if the instrumented code gets executed.

We decided to extract the code examples from the Readme files of the repository associated to the NPM Package. Readme files are usually used by developers for briefly describing what the code does, what problem it solves, how to install the application, how to build the code, etc. It is very common that developers provide code examples in the readme files to show how the code works and how to use it. This is specially true for NPM Packages, which are in general created to solve a specific problem of JavaScript development.

Obtaining code examples for a specific NPM Package is achieved in three steps:
\begin{enumerate}
  \item Obtaining the repository from the package.
  \item Retrieving the README file from the repository.
  \item Extract the code examples from the README file.
\end{enumerate}

\subsection{Repository}
The \mintinline{bash}{npm view} command shows data about a package. It is possible to retrieve a specific field of the package registry by specifying fhe field name after the package descriptor. For example to retrieve information about the \textit{lodash} package, the following command can be used: \mintinline{bash}{npm view lodash}.

For this particular case, only the url of the repository associated with the package is needed. This can be achieved by adding the correponding field name: \mintinline{bash}{npm view <PACKAGE> repository.url}.

\begin{bashinline}
$ npm view npm repository.url
git+https://github.com/npm/cli.git

$ npm view lodash repository.url
git+https://github.com/lodash/lodash.git

$ npm view jquery repository.url$
git+https://github.com/jquery/jquery.git
\end{bashinline}

\subsection{Readme files}
The url for downloading a raw file from a Github Repository is the following:

\begin{bashinline}
https://raw.githubusercontent.com/THE-REPOSITORY/master/PATH-TO-FILE
\end{bashinline}

After the repository url is extracted from the npm package, the url for downloading the readme file needs to be constructed performing some string manipulation. Finally, the readme file is obtained with a simple \mintinline{bash}{curl} or \mintinline{bash}{wget} command.

\begin{bashinline}
$ npm view abs repository.url
git+ssh://git@github.com/IonicaBizau/abs.git

$ curl -L -o readme.md --fail \
    https://raw.githubusercontent.com/IonicaBizau/abs/master/README.md
\end{bashinline}

\subsection{Code examples}
Readme files are written using Markdown\footnote{https://www.markdownguide.org}, a very common lightweight and simple markup language. GitHub or BitBucket will convert the readme files into HTML automatically and render them when accessing the repository through a web browser.

It is very common to write code examples within code blocks indicating the programming language, so that it gets highlighted with the specific syntax. The Markdown identifiers for JavaScript are \mintinline{bash}{js} or \mintinline{bash}{javascript}. The code examples are finally retrieved by filtering the content within the corresponding code blocks.

\begin{textinline}
$ cat example-readme.md
# Description
This is an example that shows how to use console.log().

```js
var a = "Hello World!";

function f(s) {
	console.log(s);
}

f(a);
```

$ cat example-readme.md | \
  sed 's/```javascript/```js/g' | \
  sed -n '/^```js/,/^```/ p' > example.js

$ node example.js
Hello World!
\end{textinline}

\section{Run-time Information Gathering} \label{run-time-information-gathering}
As shown in a simple example in \figref{fig:run-time-information-gathering-simple-example}, run-time analysis will gather information such as:

\begin{enumerate}
  \item Function \mintinline{bash}{f} got invoked with parameters \mintinline{bash}{a} and \mintinline{bash}{b} with types \mintinline{bash}{string} and \mintinline{bash}{number}.
  \item Property or method \mintinline{bash}{foo} of parameter \mintinline{bash}{a} of function \mintinline{bash}{f} was accessed within the function.
  \item Parameter \mintinline{bash}{a} of function \mintinline{bash}{f} was used as operand for operator \mintinline{bash}{==}.
\end{enumerate}

The dynamic analysis framework used for gathering this kind of information is Jalangi. As explained in \secref{sec:jalangi}, the configurable analysis modules enable programming custom callbacks that get triggered with virtually any JavaScript event. The events that are observed are:
\begin{enumerate}
  \item Binary operations, like \mintinline{bash}{==}, \mintinline{bash}{+} or \mintinline{bash}{===}.
  \item Variable declaration.
  \item Function, method, or constructor invocation.
  \item Access to an object's property.
  \item Unary operations, like \mintinline{bash}{!} or \mintinline{bash}{typeof}.
\end{enumerate}

The implementation stores these observations as entities called \textit{interactions}. As explained later in \secref{run-time-analysis}, they are used for translating, modifying and aggregating Jalangi's raw event information in order to get an application specific data representation.

The main goal of the run-time analysis is to gather information useful for determining a function's signature. Therefore, observations need to get associated with a function's argument. The implementation wraps variables around Proxy Objects to store tracking data, hereby enabling to associate the observation with a specific argument. The effect is reverted using Jalangi's callbacks to modify the behaviour of the affected operators, such as \mintinline{bash}{===} or \mintinline{bash}{typeof}.

Jalangi fails to instrument some JavaScript Libraries. No effort was made in trying to fix failing instrumentation. Failing JS Libraries were ommited from the analysis by providing a list with the names of the modules that should not be instrumented.

Each function is given an unique key, which is used as the primary key of a map where the run-time information is stored. Each function has an array of arguments and each interaction gets associated with an argument. The map is finally returned as a JSON file that can be used for later processing.

The tool is written in JavaScript and runs in Node.js within a Docker container.

\input{figures/approach/run-time-information-gathering/simple-example.tex}

\subsection{Analysis} \label{run-time-analysis}
\todo{inputValue}
\input{figures/approach/run-time-information-gathering/analysis/input-value.tex}
\input{figures/approach/run-time-information-gathering/analysis/get-field.tex}
\input{figures/approach/run-time-information-gathering/analysis/method-call.tex}
\input{figures/approach/run-time-information-gathering/analysis/used-as-argument.tex}

\todo{getField}
\todo{putField}
\todo{methodCall}
\todo{usedAsArgument}
\todo{operatorInteraction}

\todo{followingInteractions}
\todo{traces}

\subsection{Wrapper Objects}
\todo{Proxy Objects}
\todo{Primitives}
\todo{Null}
\todo{Undefined}

\subsection{Output Format}
\todo{Explicar que es un JSON con todas las interactions. Explicar estructura de cómo se forma el JSON}

\subsection{Blacklisted Modules}
\input{figures/approach/blacklisted-modules/blacklistedModules.tex}
\todo{Incluir grafico con los blacklisted modules}

### 2019-08-05 chapters/6-conclusions.tex
Add todo message for merging declaration files
Add code example for run-time information gathering

@@

\subsection{Type Inference}
\todo{Deberia ser hecho en otro modulo que no sea el runtime information. El runtime information deberia exponer unicamente los datos que le hacen falta al otro para inferir los tipos.}
\subsubsection{Variable Names}
\todo{Se puede extraer info del nombre de las variables y del nombre de los metodos, etc. La developer's intention.}

@@

>>>>

\draft{Una de las conclusiones mas importantes es que la type inference al final no es tan importante. Lo dificil es generar el declaration file como corresponde, detectar las interfaces, etc. El tipo de las variables puede, en principio, inferirse de los ejemplos de los developers. Es una aproximación bastante acertada y se atacan los otros problemas.}

\draft{Decir que todos los bloques pueden mejorarse independientemente: Extraer mejor los readme files, mejorar la instrumentation usando Babel para quedarse siempre en ES5... mejorar la generation de declaration files, etc.}

@@

\subsection{Type Inference}
\todo{Deberia ser hecho en otro modulo que no sea el runtime information. El runtime information deberia exponer unicamente los datos que le hacen falta al otro para inferir los tipos.}
\subsubsection{Return values}
\todo{El return value se podria incluir en el analysis de Jalangi, detectando las interactions que tiene etc etc. Esto no es tan facil porque no se puede simplemente inspeccionar el return value, sino que hay que saber para qué se usa. Los ejemplos podrían ser útiles}.

\subsubsection{Variable Names}
\todo{Se puede extraer info del nombre de las variables y del nombre de los metodos, etc. La developer's intention.}

@@

\todo{MERGE Declaration Files - Ver si se agrega}

### 2019-08-05 figures/approach/run-time-information-gathering/analysis/input-value.tex
Add code example for run-time information gathering

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.4\textwidth}
			\jscode{code/run-time-information-gathering/simple-examples/get-field.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[Instrumented JS code]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.58\textwidth}
			\jsoncode{code/run-time-information-gathering/simple-examples/output-get-field.json}
		\end{minipage}
	\end{lrbox}
	\subfloat[Run-time information output]{\usebox{\mintedbox}}
	\caption[\textit{getField} interaction example]{\textbf{\textit{getField} interaction example} - The accessed properties of argument \textit{a} with their type are recorded. Several additional fields and entries of the final output JSON file were ommited for simplicity.}
	\label{fig:run-time-information-gathering-get-field}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.4\textwidth}
			\jscode{code/run-time-information-gathering/simple-examples/input-value.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[Instrumented JS code]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.58\textwidth}
			\jsoncode{code/run-time-information-gathering/simple-examples/output-input-value.json}
		\end{minipage}
	\end{lrbox}
	\subfloat[Run-time information output]{\usebox{\mintedbox}}
	\caption[\textit{inputValue} interaction example]{\textbf{\textit{inputValue} interaction example} - The type of the arguments of function \textit{foo()} is recorded. Several additional fields and entries of the final output JSON file were ommited for simplicity.}
	\label{fig:run-time-information-gathering-input-value}
\end{figure}

### 2019-08-05 figures/approach/run-time-information-gathering/simple-example.tex
Add code example for run-time information gathering

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.4\textwidth}
			\jscode{code/run-time-information-gathering/simple-examples/input-value.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[Instrumented JS code]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.58\textwidth}
			\jsoncode{code/run-time-information-gathering/simple-examples/output-input-value.json}
		\end{minipage}
	\end{lrbox}
	\subfloat[Run-time information output]{\usebox{\mintedbox}}
	\caption[\textit{inputValue} interaction example]{\textbf{\textit{inputValue} interaction example} - The type of the arguments of function \textit{foo()} is recorded. Several additional fields and entries of the final output JSON file were ommited for simplicity.}
	\label{fig:run-time-information-gathering-input-value}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.4\textwidth}
			\jscode{code/run-time-information-gathering/simple-examples/simple-example.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[Instrumented JS code]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.58\textwidth}
			\jsoncode{code/run-time-information-gathering/simple-examples/output-simple-example.json}
		\end{minipage}
	\end{lrbox}
	\subfloat[Run-time information output]{\usebox{\mintedbox}}
	\caption[Simple run-time information gathering example]{\textbf{Simple run-time information gathering example} - Example code showing \textit{inputValue} and \textit{getField} interactions. Several additional fields and entries of the final output JSON file were ommited for simplicity.}
	\label{fig:run-time-information-gathering-simple-example}
\end{figure}
